\begin{Large}
\begin{center}Abstract\end{center}
\end{Large}

\noindent LibreCAD v3 development project discusses the work done in computer-aided-design. Computer-aided design (CAD) is the use of computer systems to assist in the creation, modification, analysis, or optimization of a design in engineering sciences. I explored  LibreCAD  Source  Code. LibreCAD is Free and Open Source  2D  CAD   application  that  you  can  download  and  install  for  free.  There  is  a  large base  of  satisfied  LibreCAD   users  worldwide,  and  it  is  available  in  more  than  20  languages  and  for  all major  operating  systems,  including  Microsoft  Windows,  Mac  OS  X  and  Linux .  Librecad  is  an  application  for  computer  aided  design  in  two dimensions  .  With  librecad   you   can  create  technical  drawings  such  as  plans  for  buildings,  interiors, mechanical parts or schematics and diagrams. Basically, LibreCAD is used to make 2D design. \\

\noindent LibreCAD was forked from QCAD Software 12 years ago. Since then technologies changed a lot and LibreCAD was on a Quite old code base. We have designed a new version of LibreCAD Code named as v3 updating the LibreCAD to new technologies and the real world exposure enhancing the internals of LibreCAD to be able to handle Large files efficiently and a MVC like modular approach so as to make v3 capable of integration into other softwares ( BRL-CAD being a live example of the use case except the LibreCAD itself).

\noindent Also, this project is completely open source and the entire code is available to the user as and when required. There is also Complete developer's Documentation as well as User manual alongwith it that helps using it a lot easier.
